An Imaging Search for Post-Main-Sequence Planets of Sirius B

### 2021-11-19 paper/paper.tex
update paper with fresh revisions

@@

\begin{abstract}
Discovery and characterization of post-main-sequence planets is essential to study planetary system evolution and planet-star interactions during the most critical phases of stellar evolution. We present deep imaging of Sirius B, the closest and brightest white dwarf, in order to constrain post-main-sequence planetary evolution in the Sirius system. We use Keck/NIRC2 in \Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 using the technique of angular differential imaging. Our observations are speckle-limited out to \qty{1}{\au} and background-limited beyond. The 5$\sigma$ detection limits from our best performing epoch are \numrange{17}{20.4} \Lp absolute magnitude. We consider multiple planetary formation pathways in the context of Sirius B's evolution to derive mass sensitivity limits, and achieve sub-Jupiter sensitivities at sub-AU separations, reaching \qtyrange{1.6}{2.4}{\jupitermass} at \qty{0.5}{\au} down to a sensitivity of \qtyrange{0.7}{1.2}{\jupitermass} at \textgreater\qty{1}{\au}. Consistent with previous results, we do not detect any companions around Sirius B. Our strong detection limits demonstrate the potential of using high-contrast imaging to characterize nearby white dwarfs.
\end{abstract}

@@

In recent decades thousands of exoplanets have been discovered orbiting stars that will eventually leave the stability of the main-sequence (MS) \citep{akesonNASAExoplanetArchive2013}. The fate of planets around these stars beyond the MS is uncertain due to the large expansion, stellar winds, and high irradiation encountered during giant branch evolution \citep{verasPostmainsequencePlanetarySystem2016}. Despite this, direct evidence from white dwarf pollution \citep{juraExternallyPollutedWhite2007,xuSpitzerObservationsWhite2012}, debris disks \citep{deruyterKeplerianDiscsPostAGB2006,zuckermanAncientPlanetarySystems2010,koesterFrequencyPlanetaryDebris2014}, and substellar companions \citep[e.g.,][]{luhmanDiscoveryCandidateCoolest2011,vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} culminate to suggest planetary systems beyond the MS are more common than previously thought. Discovery and characterization of post-MS planets is essential to study planetary system evolution and planet-star interactions during the most critical phases of stellar evolution.

The evolution of intermediate-mass stars (\qtyrange{1}{8}{\solarmass}) comprises a violent and relatively brief period of giant branch evolution before all nuclear fusion ends and the stars become white dwarfs. As the MS star runs out of hydrogen to burn in its core, it expands to 100s of times its size, engulfing any companions within the stellar radius. When helium fusion ignites the giant star becomes three to four orders of magnitude brighter than its MS progenitor, causing stellar winds and strong irradiation. Eventually the star runs out of fuel and concludes its nuclear burning, becoming a white dwarf. The white dwarf begins cooling, becoming three to four orders of magnitude dimmer than its MS progenitor.

There is limited knowledge of planetary systems around evolved stars. The pathway for a \textit{first-generation} planet to survive around a post-MS host is violent and uncertain. During giant branch evolution, the planet needs to escape engulfment as well as tidal shredding from its inflated host \citep{burleighImagingPlanetsNearby2002a,nordhausOrbitsLowmassCompanions2013}. Planets which survive their hosts' inflation are subject to stellar winds and high luminosity, which causes adiabatic orbit expansion (with the potential for destabilizing the orbit), chemical enrichment of the circumstellar environment with metals and dust, and strong irradiation \citep{mustillForetellingsRagnarokWorldengulfing2012,verasPostmainsequencePlanetarySystem2016}. Numerical simulations suggest that a giant planet needs to be $\gtrsim$\qty{5}{\au} from a solar-like host to escape expansion and tidal effects \citep{spiegelJupiterWillBecome2012,nordhausOrbitsLowmassCompanions2013}. When combined with adiabtatic orbit expansion, this creates a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{10}{\au}.

Recent discoveries of exoplanets in ``forbidden'' formation regions \citep{vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} suggest evidence for a class of \textit{second-generation} companions. \citet{peretsSecondGenerationPlanets2010,peretsPlanetsEvolvedBinary2011} describe a planetary formation pathway where, in multi-star systems, the stellar ejecta from an evolving giant star forms a protoplanetary disk around a separate star (or, in fact, the whole system). These disks serve as reservoirs of material and energy for planet formation, and new planets could form from a first-generation planet acting as a seed. Such disks would have lifetimes of \qtyrange{1}{100}{\mega\year} which is commensurate with both ``hot'' and ``cold''-start planetary formation timescales \citep{marleyLuminosityYoungJupiters2007,spiegelSpectralPhotometricDiagnostics2012a}. Another formation pathway considers the chaotic evolution of companion orbits due to stellar mass loss in the presence of multiple bodies. \citet{peretsTripleEvolutionDynamical2012} describe this interaction for triplet systems in detail (the ``triple evolution dynamical interaction'', or TEDI). \citet{kratterStarHoppersPlanet2012} explore similar dynamical interactions in the restricted three-body problem and concluded up to $\sim$10\% of all white dwarf binaries might contain ``star-hopper'' planets which migrate between the stars.

Previous searches for substellar companions around white dwarfs \citep[e.g.,][]{debesAreThereUnstable2002,hoganDODOSurveyII2009,luhmanDiscoveryCandidateCoolest2011,xuExtremeAOSearchGiant2015a} have primarily focused on detecting wide-orbit planets which survived the giant branch evolution of their hosts. Recent evidence and theories, though, suggest ``forbidden'' regions of planetary evolution are worth investigating for exotic post-MS planets. These planets would provide crucial insight into planetary system evolution and planet-star interactions during giant branch evolution.

In the rest of this report, we will discuss high-contrast imaging as a detection technique for post-MS systems (\Cref{sec:imaging}). We will introduce the Sirius system as a potential candidate for post-MS planets, along with previous studies of white dwarf Sirius B (\Cref{sec:sirius}). We will detail our 2020 near-infrared observations of Sirius B with Keck/NIRC2, as well as our processing steps and statistical analysis for companion detection (\Crefrange{sec:obs}{sec:analysis}). Lastly, we will discuss our results within the context of Sirius and post-MS systems as well as future directions for post-MS imaging (\Crefrange{sec:results}{sec:conclusion}).

\section{Directly imaging post-MS systems}\label{sec:imaging}

High-contrast imaging is a powerful, but challenging, technique for discovering and characterizing exoplanets. Giant exoplanets are most easily detected by their thermal emission, which peaks in the infrared and decreases exponentially as the planet ages \citep{fortneyGiantPlanetInterior2010}. The typical astrophysical flux ratios (contrasts) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traubDirectImagingExoplanets2010}. The close angular separations of exoplanets make it difficult to disentangle planet-light from the stellar diffraction pattern. This problem is exacerbated on the ground as the effects of atmospheric seeing further degrade the sensitivity to exoplanets. High-contrast imaging typically comprises large-aperture telescopes, adaptive optics (AO), coronagraphy, high-gain, low-read-noise detectors, observational techniques, and post-processing techniques to overcome the challenges in detecting the faint exoplanet signal.

 Using large-aperture telescopes provides greater collecting power and angular resolution. AO corrects, to an extent, the effects of atmospheric seeing and instrumental noise (speckles) by measuring wavefront errors and cancelling them out with dynamical optics, like a deformable mirror. Wavefront errors are measured from a wavefront sensor which typically is illuminated by the target itself. The high loop rates of AO, especially on the ground ($\sim$\qty{100}{\hertz} to \qty{1}{\kilo\hertz}), makes Poisson photon noise the limiting factor for AO, which limits the efficacy of faint imaging targets. AO correction is necessary for maintaining the necessary angular resolution and sensitivity for exoplanet imaging, as well as keeping the stellar point-spread-function (PSF) centered on a coronagraph, if present.

Coronagraphs are designed to control and attenuate the diffraction of starlight through the telescope while allowing off-axis exoplanet light to pass unperturbed. Coronagraphs are extremely sensitive to wavefront errors, particularly tip-tilt pointing errors, necessitating high-quality AO correction. Coronagraphs have an inner working angle, the separation where stellar throughput is halved, which is analagous to the full-width at half-maximum (FWHM) of a non-coronagraphic PSF. The inner working angle determines how close we can probe to the stars, and it fundamentally limits imaging searches to nearby systems, whose projected separations are closer to solar-system scales.

Exoplanets are faint enough that only a few photons per second reach the detector \citep{traubDirectImagingExoplanets2010}, which makes High-gain, low-read-noise detectors paramount for direct imaging. Observational techniques, like angular differential imaging \citep{maroisAngularDifferentialImaging2006}, spatially decorrelate speckles to improve the noise attenuation of long observations. Post-processing techniques like PSF subtraction remove the stellar diffraction pattern, but at the risk of removing exoplanet signal. Altogether, these techniques have proven sufficient for ground-based telescopes to image giant planets outside our solar system.

White dwarfs are interesting targets for direct imaging- they are three to four orders of magnitude fainter than their MS progenitors, reducing the contrast necessary to detect a companion. The lack of spectral features of white dwarfs \citep{schatzmanTheorieDebitEnergie1945} makes them difficult targets for the radial velocity technique. The small stellar radii of white dwarfs lowers the transit probability significantly, although detections of substellar companions around white dwarfs have been made \citep[e.g.,][]{vanderburgGiantPlanetCandidate2020}. The faintness of white dwarfs proves challenging due to the high signal-to-noise ratio (S/N) required by the AO. This is exacerbated on ground-based telescopes which require extreme AO to counteract the effects of atmospheric seeing. This constrains potential companion searches to relatively bright targets ($m^R\lesssim$ 13). Implicitly, this also limits searches to nearby white dwarfs ($d\sim$\qty{25}{\parsec}, \citealp{holberg25ParsecLocal2016}), which is beneficial for imaging because the limited inner working angle of the instrumentation will project to closer separations around closer stars.

@@

One fascinating target for post-MS observations is Sirius B, the closest and brightest white dwarf to the sun. The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1V star and Sirius B, a DA white dwarf with a \qty{50}{\year} orbit \citep{gaiacollaborationGaiaMission2016,bondSiriusSystemIts2017,gaiacollaborationGaiaEarlyData2021}. As mentioned previously, the proximity and intrinsic faintness of Sirius B (compared to a MS star) make it compelling for direct imaging. Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortneyGiantPlanetInterior2010}.

Sirius is one of the oldest studied star systems; the breadth and depth of knowledge about the binary gives exceptional precision for characterizing the circumstellar environment. Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwersOrbitSirius1864}. Most recently, \citet{bondSiriusSystemIts2017} used Hubble Space Telescope (HST) along with old photographic plates to compile the most precise orbital solution for Sirius to date. They derived dynamical masses using their orbital solution and Hipparcos parallaxes: \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively. A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holmanLongTermStabilityPlanets1999}. \citet{bondSiriusSystemIts2017} calculate the longest period stable companion around Sirius B is \qty{1.79}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.

@@

We adopt the system age derived in \citet{cummingsWhiteDwarfInitialFinal2018} using MIST isochrones of \qty{225}{\mega\year}, which implies a ZAMS to TGB age of \qty{99}{\mega\year}. These age determinations are limited both by the precision of the stellar parameters as well as the stellar evolution model. The spread of ages derived by \citet{cummingsWhiteDwarfInitialFinal2018} from different models is $\sim$\qty{10}{\mega\year}. Determining stellar ages is not trivial, and for many systems an accurate age is impossible to constrain. This age uncertainty of $\sim$4\% is exceptional, even compared to the $\sim$10\% uncertainty of stars found in young moving groups. The values for our adapted and derived parameters values are compiled in \Cref{tbl:system}.

One of the peculiarities of the Sirius system is its large eccentricity, $e\sim0.6$ \citep{bondSiriusSystemIts2017}. If we assume the orbital expansion due to Sirius B's evolution was adiabatic, we can calculate the initial semi-major axis of the binary
\begin{equation}
    a_i = a_f \frac{M_{B,f} + M_{A,f}}{M_{B,i} + M_{A,i}}
\end{equation}
where $a$ is the system semi-major axis, $M_A$ and $M_B$ are the respective stellar masses, and subscripts $i$ and $f$ correspond to the initial (MS) versus final (post-MS) states \citep{jeansCosmogonicProblemsAssociated1924}. The current semi-major axis of the binary is \qty{20}{\au}, and assuming negligible mass transfer between the two stars, the initial semi-major axis would be \qty{8.6\pm1.3}{\au}. If the orbit expansion was indeed adiabatic, the eccentricity would be the same before and after evolution. In this case, the periastron of Sirius A and B would be \qty{3.52\pm0.52}{\au}. \citet{verasPostmainsequencePlanetarySystem2016} tabulated the maximum stellar radius of intermediate mass stars during their giant evolution, from which we interpolate a maximum radius for Sirius B of \qty{5.104\pm0.075}{\au}. This means Sirius A certainly interacted with Sirius B and may have had a common envelope stage. Mass transfer and tidal circularization would be expected, however the present-day eccentricity provide contrary evidence.

\citet{bonacicmarinovicOrbitalEccentricitiesBinary2008} propose an explanation for the lack of tidal circularization called ``tidal-pumping,'' but neglect to address the observed slow rotation speed of Sirius A \citep{grayPreciseRotationRates2014,takedaRotationalVelocitySirius2020a}, which would be expected to increase with mass transfer to conserve total angular momentum in the binary. \citet{peretsTripleEvolutionDynamical2012} suggest the present eccentricity could be due to the chaotic expulsion of third body between \qtyrange{0.6}{5.5}{\solarmass}. \citet{kratterStarHoppersPlanet2012} point out, though, that the most probable outcome of a planetary-mass companion in a chaotic orbital evolution is collision with one of the binary components. If Sirius B ejected a first-generation companion during its giant branch evolution, we estimate a $\sim$70\% probability of the planet colliding with Sirius A \citep[Fig. 7]{kratterStarHoppersPlanet2012}, although this is far from disqualifying the potential for orbital capture. This is an interesting explanation for the chemical peculiarities of Sirius A's atmosphere \citep{landstreetAbundancesElementsHe2011a,takedaRotationalVelocitySirius2020a}. The variety in these studies show the necessity to consider multiple, potentially exotic formation pathways for planetary candidates.

@@

% \begin{deluxetable}{ccccc}
%     \tabletypesize{\small}
%     \tablecaption{Observing parameters for the three epochs of data. All observations were carried out using the NIRC2 narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) in \Lp-band (\qty{3.776}{\micro\meter}). Observation time is based on the frames that were selected for processing. Seeing values were measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session. Seeing values, temperature, and water vapor measurements were all taken from the Maunakea weather center forecast archive.
%     \label{tbl:obs}}
%     \tablehead{
%         \colhead{Epoch} &
%         \colhead{2020-02-4} &
%         \colhead{2020-11-21} &
%         \colhead{2020-11-28} &
%         \colhead{}
%     }
%     \startdata
%     Sirius B offset & 11.20 & 11.27 & 11.27 & \unit{\arcsecond}  \\
%     Sirius B PA & 67.90 & 66.42 & 66.38 & \unit{\degree} \\
%     Obs. time & 1.44 & 2.91 & 2.44 & hr \\
%     FOV rotation & 60.1 & 91.4 & 80.4 & \unit{\degree} \\
%     FWHM & 79.9 & 76.4 & 82.2 & \unit{\milliarcsecond} \\
%     Seeing & 0.936 & 0.871 & 1.23 & \unit{\arcsecond} \\
%     Temp & 0.0 & 0.8 & -1.5 & \unit{\celsius} \\
%     PWV & 0.7 & 3.5 & 3.0 & \unit{\milli\meter}
%     \enddata
% \end{deluxetable}

\begin{figure}
    \centering
    \epsscale{1.1}
    \plotone{spike}
    \caption{Scattered light from Sirius A is present in our FOV around Sirius B as shown by this diffraction spike  sweeping across a calibrated science frame of Sirius B from the first epoch. Despite Sirius B's separation of \ang{;;11}, the overwhelming brightness of Sirius A impedes observations of Sirius B.}
    \label{fig:spike}
\end{figure}

@@

\begin{figure*}
    \centering
    \plotone{detection_maps}
    \caption{\textbf{top row:} The \textit{significance} maps for each epoch accounting for small-sample statistics \citep{mawetFundamentalLimitationsHigh2014}. Typically a critical value for detection is 5. \textbf{bottom row:} The STIM maps for each epoch calculated from each residual cube. The STIM probability has a typical cutoff threshold of 0.5 for significant detections. The inner two FWHMs are masked out for each map.}
    \label{fig:detection}
\end{figure*}

>>>>

\received{August 13, 2021}
\revised{\today}

@@

\begin{abstract}
We present deep imaging of Sirius B, the closest and brightest white dwarf, to constrain post-main-sequence planetary evolution in the Sirius system. We use Keck/NIRC2 in \Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 using the technique of angular differential imaging. Our observations are speckle-limited out to \qty{1}{\au} and background-limited beyond. The 5$\sigma$ detection limits from our best performing epoch are \numrange{17}{20.4} \Lp absolute magnitude. We consider multiple planetary formation pathways in the context of Sirius B's evolution to derive mass sensitivity limits, and achieve sub-Jupiter sensitivities at sub-AU separations, reaching \qtyrange{1.6}{2.4}{\jupitermass} at \qty{0.5}{\au} down to a sensitivity of \qtyrange{0.7}{1.2}{\jupitermass} at \textgreater\qty{1}{\au}. Consistent with previous results, we do not detect any companions around Sirius B. Our strong detection limits demonstrate the potential of using high-contrast imaging to characterize nearby white dwarfs.
\end{abstract}

@@

In recent decades thousands of exoplanets have been discovered orbiting stars that will eventually leave the stability of the main-sequence (MS) \citep{akesonNASAExoplanetArchive2013}. The eventual fate of planets around these stars is uncertain due to the large expansion, stellar winds, and high irradiation encountered during giant branch evolution \citep{verasPostmainsequencePlanetarySystem2016}. Despite this, direct evidence from white dwarf pollution \citep{juraExternallyPollutedWhite2007,xuSpitzerObservationsWhite2012}, debris disks \citep{deruyterKeplerianDiscsPostAGB2006,zuckermanAncientPlanetarySystems2010,koesterFrequencyPlanetaryDebris2014}, and substellar companions \citep[e.g.,][]{luhmanDiscoveryCandidateCoolest2011,vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} culminate to suggest planetary systems beyond the MS are more common than previously thought. Discovery and characterization of post-MS planets is essential to study planetary system evolution and planet-star interactions during the most critical phases of stellar evolution.

The evolution of intermediate-mass stars (\qtyrange{1}{8}{\solarmass}) comprises a violent and relatively brief period of giant branch evolution before all nuclear fusion ends and the stars become white dwarfs. As the main-sequence star runs out of hydrogen to burn in its core, it expands to 100s of times its size, engulfing any companions within the stellar radius. When helium fusion ignites, the giant star becomes three to four orders of magnitude brighter, causing stellar winds and strong irradiation. Eventually, the star runs out of fuel and concludes its nuclear burning, becoming a white dwarf. The white dwarf begins cooling, becoming three to four orders of magnitude dimmer than its MS progenitor.

There is limited knowledge of planetary systems around evolved stars. The pathway for a \textit{first-generation} planet to survive around a post-MS host is violent and uncertain. During giant branch evolution, the planet needs to escape engulfment as well as tidal shredding from its inflated host \citep{burleighImagingPlanetsNearby2002a,nordhausOrbitsLowmassCompanions2013}. Planets which survive their hosts' inflation are privy to the effects of stellar winds and the high luminosities of asymptotic giant stars \citep{mustillForetellingsRagnarokWorldengulfing2012,mustillMainsequenceProgenitorConfigurations2013,verasPostmainsequencePlanetarySystem2016}. The stellar winds will chemically enrich the circumstellar environment with metals and dust, and the high luminosity and proximity to the stellar surface will cause strong irradiation, and therefore heating \citep{spiegelJupiterWillBecome2012}. The mass-loss from the stellar winds can adiabatically expand a planet's orbit \citep{jeansCosmogonicProblemsAssociated1924}, potentially destabilizing the orbit and chaotically ejecting the planet \citep{kratterStarHoppersPlanet2012}. Numerical simulations suggest that a giant planet needs to be $\gtrsim$\qty{5}{\au} from a solar-like host to escape expansion and tidal effects \citep{spiegelJupiterWillBecome2012,nordhausOrbitsLowmassCompanions2013}. When combined with adiabatic orbit expansion, this creates a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{10}{\au}.

Recent discoveries of exoplanets in ``forbidden'' formation regions \citep{vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} suggest evidence for a class of \textit{second-generation} companions. \citet{peretsSecondGenerationPlanets2010,peretsPlanetsEvolvedBinary2011} describe a planetary formation pathway where, in multi-star systems, the stellar ejecta from an evolving giant star forms a protoplanetary disk around another star (or, in fact, the whole system). These disks serve as reservoirs of material and energy for planet formation, which could be kick-started by a first-generation planet acting as a seed. Such disks would have lifetimes of \qtyrange{1}{100}{\mega\year} which is commensurate with both gravitational-instability (``hot start'') and core-accretion (``cold start'') formation theories \citep{marleyLuminosityYoungJupiters2007,spiegelSpectralPhotometricDiagnostics2012a}. Another formation pathway considers the chaotic evolution of companion orbits due to stellar mass loss in the presence of multiple bodies. \citet{peretsTripleEvolutionDynamical2012} describe this interaction for triplet systems in detail (the ``triple evolution dynamical interaction'', or TEDI). \citet{kratterStarHoppersPlanet2012} explore similar dynamical interactions in the restricted three-body problem and concluded up to $\sim$10\% of all white dwarf binaries might contain ``star-hopper'' planets which migrate between the stars.

Previous searches for substellar companions around white dwarfs \citep[e.g.,][]{debesAreThereUnstable2002,hoganDODOSurveyII2009,luhmanDiscoveryCandidateCoolest2011,xuExtremeAOSearchGiant2015a} have primarily focused on detecting wide-orbit planets which survived the giant branch evolution of their hosts. Recent evidence and theoretical works, though, suggest ``forbidden'' regions of planetary evolution are worth investigating for exotic post-MS planets. These planets would provide crucial insight into planetary system evolution and planet-star interactions during giant branch evolution.

Direct imaging is well-suited for finding planets around white dwarfs due to the intrinsic faintness of the host (compared to a MS star) and lack of spectral features for radial velocity studies \citep{burleighImagingPlanetsNearby2002a}. With direct imaging, exoplanets can be detected and characterized independently from the orbital period of the planet, the stellar radius, or stellar spectrum, which makes it powerful compared to broadband photometric analysis or transit photometry methods. High-contrast imaging pushes direct imaging to its limits using large-aperture telescopes, adaptive optics, coronagraphy, low-noise detectors, image-processing, and observational techniques. Despite the power of high-contrast imaging, very few observations have been carried out for white dwarfs (a recent example is \citealt{pathakHighContrastImaging2021}).

Exoplanets are faint enough that only a few photons per second reach the detector. The host stars are many orders of magnitude brighter than the thermal emission of giant planets ($\sim10^{\text{-}8}$) and have close angular separations, which means planets are easily washed out by the stellar diffraction pattern \citep{traubDirectImagingExoplanets2010}. In addition, atmospheric seeing and instrumental aberrations greatly reduce the sensitivity to exoplanets due to the manifestation of quasi-random perturbations of the instrumental point-spread function (speckles, see \citealp{guyonExtremeAdaptiveOptics2018}). Adaptive optics (AO) corrects a large percentage of the effects of speckles but has decreasing efficacy for dim targets due to the photon-limited nature of modern AO instrumentation. AO is also paramount for enabling coronagraphy, which attenuates on-axis starlight while transmitting off-axis signal, up to some inner working angle.

Typical high-contrast targets are nearby young objects observed in the near-infrared. Younger planets are brighter, thanks to their latent formation heat \citep{fortneyGiantPlanetInterior2010}, which reduces the star-planet contrast, and observing them in the near-infrared corresponds with their peak blackbody emission. Nearby targets have larger angular separations between potential planets and their hosts, which makes it easier to separate the signals. Nearby targets are also intrinsically brighter, enabling effective AO control. White dwarfs are atypical high-contrast targets due to their age and sparsity, but their relative faintness is compelling for the reduced contrast. In addition, a post-MS planet would be much younger than the system age of a white dwarf and would therefore still retain a large portion of its latent heat, further motivating high-contrast searches of nearby white dwarfs.

We set out in this work to perform high-contrast observations of Sirius B for post-MS planets. In the rest of this report, we will introduce the Sirius system as a potential candidate for post-MS planets, along with previous studies of white dwarf Sirius B (\Cref{sec:sirius}). We will detail our 2020 near-infrared observations of Sirius B with Keck/NIRC2, as well as our processing steps and statistical analysis for companion detection (\Crefrange{sec:obs}{sec:analysis}). Lastly, we will discuss our results within the context of Sirius and post-MS systems, as well as future directions for post-MS imaging (\Crefrange{sec:results}{sec:conclusion}).

% High-contrast imaging is a powerful, but challenging, technique for discovering and characterizing exoplanets. Giant exoplanets are most easily detected by the thermal emission of their latent formation heat, which peaks in the infrared and decreases as the planet ages \citep{fortneyGiantPlanetInterior2010}. The typical astrophysical flux ratios (contrasts) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traubDirectImagingExoplanets2010}. The close angular separations of exoplanets from their host stars make it difficult to disentangle planet-light from the stellar diffraction pattern. This problem is exacerbated on the ground as the effects of atmospheric seeing further degrade the sensitivity to exoplanets. High-contrast imaging typically comprises large-aperture telescopes, adaptive optics (AO), coronagraphy, low-noise detectors, observational techniques, and image-processing to overcome the challenges in detecting the faint exoplanet signal.

% Using large-aperture telescopes provides greater collecting power and angular resolution. AO corrects, to an extent, the effects of atmospheric seeing and instrumental noise (speckles) by measuring wavefront errors and cancelling them out with dynamical optics, like a deformable mirror. Wavefront errors are measured from a wavefront sensor which typically is illuminated by the target itself. The high loop rates of AO, especially on the ground ($\sim$\qty{100}{\hertz} to \qty{1}{\kilo\hertz}), makes Poisson photon noise the limiting factor for AO, which limits the efficacy of faint imaging targets \citep{guyonExtremeAdaptiveOptics2018}. AO correction is necessary for maintaining the necessary angular resolution and sensitivity for exoplanet imaging, as well as keeping the stellar point-spread-function (PSF) centered on a coronagraph, if present.

% Coronagraphs are designed to control and attenuate the diffraction of starlight through the telescope while allowing off-axis exoplanet light to pass unperturbed. Coronagraphs are extremely sensitive to wavefront errors, particularly tip-tilt pointing errors, necessitating high-quality AO correction. Coronagraphs have an inner working angle, the separation where stellar throughput is halved, which is analogous to the full-width at half-maximum (FWHM) of a non-coronagraphic PSF. The inner working angle determines how close we can probe to the stars, and it fundamentally limits imaging searches to nearby systems, whose projected separations are closer to solar-system scales.

% Exoplanets are faint enough that only a few photons per second reach the detector \citep{traubDirectImagingExoplanets2010}, which makes high-gain, low-read-noise detectors paramount for direct imaging. Observational techniques, like angular differential imaging \citep{maroisAngularDifferentialImaging2006}, spatially decorrelate speckles to improve the noise attenuation of long observations. Post-processing techniques like PSF subtraction remove the stellar diffraction pattern, but at the risk of removing exoplanet signal. Altogether, these techniques have proven sufficient for ground-based telescopes to image giant planets outside our solar system.

% White dwarfs are interesting targets for direct imaging- they are three to four orders of magnitude fainter than their MS progenitors, reducing the contrast necessary to detect a companion. The lack of spectral features in white dwarfs \citep{schatzmanTheorieDebitEnergie1945} makes them difficult targets for the radial velocity technique. The small stellar radii of white dwarfs lowers the transit probability significantly, although detections of substellar companions around white dwarfs have been made \citep[e.g.,][]{vanderburgGiantPlanetCandidate2020}. The intrinsic faintness of white dwarfs proves challenging due to the high signal-to-noise ratio (S/N) required by AO. This is exacerbated on ground-based telescopes which require extreme AO to counteract the effects of atmospheric seeing. This constrains potential companion searches to relatively bright targets ($m^R\lesssim$ 13). Implicitly, this also limits searches to nearby white dwarfs ($d\sim$\qty{25}{\parsec}, \citealp{holberg25ParsecLocal2016}), which is beneficial for imaging because the limited inner working angle of the instrumentation will project to closer separations around closer stars.

@@

One fascinating target for post-MS observations is Sirius B, the closest and brightest white dwarf to the sun. The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, a $J=$-1.36 magnitude A1V star, and Sirius B, a DA white dwarf with a \qty{50}{\year} orbit \citep{gaiacollaborationGaiaMission2016,bondSiriusSystemIts2017,gaiacollaborationGaiaEarlyData2021}. As mentioned previously, the proximity and intrinsic faintness of Sirius B (compared to a MS star) make it compelling for direct imaging. Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortneyGiantPlanetInterior2010}.

Sirius is one of the oldest studied star systems; the breadth and depth of knowledge about the binary gives exceptional precision for characterizing the circumstellar environment. Most recently, \citet{bondSiriusSystemIts2017} used Hubble Space Telescope (HST) along with old photographic plates to compile the most precise orbital solution for Sirius to date. Their astrometric uncertainties are over an order of magnitude improved from the visual orbit derived by \citet{vandenbosOrbitSiriusADS1960}. Following the procedure of \citet{gatewoodStudySirius1978}, \citet{bondSiriusSystemIts2017} derived dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively. A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holmanLongTermStabilityPlanets1999}. \citet{bondSiriusSystemIts2017} calculated the longest stable companion period around Sirius B to be \qty{1.8}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.

@@

We adopt the system age derived in \citet{cummingsWhiteDwarfInitialFinal2018} using MIST isochrones of \qty{225}{\mega\year}, which implies a ZAMS to TGB age of \qty{99}{\mega\year}. These age determinations are limited both by the precision of the stellar parameters as well as the stellar evolution model. The spread of ages derived by \citet{cummingsWhiteDwarfInitialFinal2018} from different models is $\sim$\qty{10}{\mega\year}. Determining stellar ages is challenging, and our age uncertainty of $\sim$4\% is exceptional compared to those typically obtained by dynamical analysis of young moving groups ($\sim$10\%) or gyrochronology ($\sim$15\%). The values for our adapted and derived parameters are compiled in \Cref{tbl:system}.

One of the peculiarities of the Sirius system is its large eccentricity, $e\sim0.6$ \citep{bondSiriusSystemIts2017}. If we assume the orbital expansion due to Sirius B's evolution was adiabatic, we can calculate the initial semi-major axis of the binary
\begin{equation}
    a_i = a_f \frac{M_{B,f} + M_{A,f}}{M_{B,i} + M_{A,i}}
\end{equation}
where $a$ is the system semi-major axis, $M_A$ and $M_B$ are the respective stellar masses, and subscripts $i$ and $f$ correspond to the initial (MS) versus final (post-MS) states \citep{jeansCosmogonicProblemsAssociated1924}. The current semi-major axis of the binary is \qty{20}{\au}, and assuming negligible mass transfer between the two stars, the initial semi-major axis would be \qty{8.6\pm1.3}{\au}. If the orbit expansion was indeed adiabatic, the eccentricity would be the same before and after evolution. In this case, the periastron of Sirius A and B would be \qty{3.52\pm0.52}{\au}. \citet{verasPostmainsequencePlanetarySystem2016} tabulated the maximum stellar radius of intermediate-mass stars during their giant evolution, from which we interpolate a maximum radius for Sirius B of \qty{5.104\pm0.075}{\au}. This means Sirius A certainly interacted with Sirius B and may have had a common envelope stage. Mass transfer and tidal circularization would be expected; however, the present-day eccentricity provides contrary evidence.

\citet{bonacicmarinovicOrbitalEccentricitiesBinary2008} propose an explanation for the lack of tidal circularization called ``tidal-pumping,'' but neglect to address the observed slow rotation speed of Sirius A \citep{grayPreciseRotationRates2014,takedaRotationalVelocitySirius2020a}, which would be expected to increase with mass transfer to conserve total angular momentum in the binary. \citet{peretsTripleEvolutionDynamical2012} suggest the present eccentricity could be due to the chaotic expulsion of a third body between \qtyrange{0.6}{5.5}{\solarmass}. \citet{kratterStarHoppersPlanet2012} point out, though, that the most probable outcome of a planetary-mass companion in a chaotic orbital evolution is a collision with one of the binary components. If Sirius B ejected a first-generation companion during its giant branch evolution, we estimate a $\sim$70\% probability of the planet colliding with Sirius A \citep[Fig. 7]{kratterStarHoppersPlanet2012}, although this is far from disqualifying the potential for orbital capture. This is an interesting, although uncertain, explanation for the peculiar surface chemical abundances found on Sirius A \citep{landstreetAbundancesElementsHe2011a,takedaRotationalVelocitySirius2020a}. The variety in these studies shows the necessity to consider multiple, potentially exotic formation pathways for planetary candidates.

@@

\begin{figure}
    \centering
    \epsscale{1.2}
    \plotone{spike}
    \caption{Scattered light from Sirius A is present in our FOV around Sirius B as shown by this diffraction spike  sweeping across a calibrated science frame of Sirius B from the first epoch. Despite Sirius B's separation of \ang{;;11}, the overwhelming brightness of Sirius A impedes observations of Sirius B.}
    \label{fig:spike}
\end{figure}

@@

\begin{figure*}
    \centering
    \plotone{detection_maps}
    \caption{\textbf{top row:} The \textit{significance} maps for each epoch accounting for small-sample statistics \citep{mawetFundamentalLimitationsHigh2014}. Typically, a critical value for detection is 5. \textbf{bottom row:} The STIM maps for each epoch calculated from each residual cube. The STIM probability has a typical cutoff threshold of 0.5 for significant detections. The inner two FWHMs are masked out for each map.}
    \label{fig:detection}
\end{figure*}
